---
title: "p8105_hw1_xh2601"
author: "Samantha Xinwei Han"
date: "2025-09-20"
output: github_document
---

## Problem 1

#### Step 1. Install moderndive package in Console

#### Step 2. Load library and data set
```{r}
# load the moderndive library
library(moderndive)
# load the tidyverse library to use ggplot
library(tidyverse)
```

```{r}
# load the early_january_weather dataset
data("early_january_weather")
# list all variable names in the dataset
names(early_january_weather)
```

#### Step 3. Review data and write description
Description: After reviewing the data through *?early_january_weather* and *View(early_january_weather)* in Console, I learned that there are 15 variables in this dataset:  
origin, year, month, day, hour, temp, dewp, humid, wind_dir, wind_speed, wind_gust, precip, pressure, visib, time_hour.

origin: EWR airport;  
year: in the year of 2013;  
month: in the month of January;
day: for the first 15 days in January;  
hour: for each hour of the day;  
temp: temperature in that hour in Fahrenheit;  
dewp: dewpoint in that hour in Fahrenheit;  
humid: relative humidity;  
wind_dir: wind direction in degrees;  
wind_speed: wind speed in mph;  
wind_gust: wind gust speed in mph;  
precip: precipitation in inches;  
pressure: sea level pressure in millibars;  
visib: visibility in miles;  
time_hour: date and time combined.

The size of this dataset is `r nrow(early_january_weather)` rows and `r ncol(early_january_weather)` columns;  
and the mean temperature is `r mean(early_january_weather$temp)` degrees in Fahrenheit.

#### Step 4. Make a plot

```{r}
# making a scatter plot, x is "time_hour", y is "temp", and colored based on "humid"
ggplot(early_january_weather, aes(x = time_hour, y = temp, color = humid)) + geom_point()
# export the scatter plot as a .jpg file
ggsave("scatterplot_temp_by_time.jpg")
```

Description:  We can see from the scatter plot that the overall temperature went up as January progressed, and the humidity levels were generally higher as the temperature increased. We can also observe that the temperature shifted within each day, indicating the temperature dropped at night and rose during the day.




