---
title: "p8105_hw1_xh2601"
author: "Samantha Xinwei Han"
date: "2025-09-20"
output: github_document
---

## Problem 1

#### Step 1. Install moderndive package in Console

#### Step 2. Load library and data set
```{r}
# load the moderndive library
library(moderndive)
```

```{r}
# load the early_january_weather dataset
data("early_january_weather")

# list all variable names in the dataset
names(early_january_weather)
```

#### Step 3. Review data and write description
Description: After reviewing the data through *?early_january_weather* and *View(early_january_weather)* in Console, I learned that there are 15 variables in this dataset:  
origin, year, month, day, hour, temp, dewp, humid, wind_dir, wind_speed, wind_gust, precip, pressure, visib, time_hour.

origin: EWR airport;  
year: in the year of 2013;  
month: in the month of January;
day: for the first 15 days in January;  
hour: for each hour of the day;  
temp: temperature in that hour in Fahrenheit;  
dewp: dewpoint in that hour in Fahrenheit;  
humid: relative humidity;  
wind_dir: wind direction in degrees;  
wind_speed: wind speed in mph;  
wind_gust: wind gust speed in mph;  
precip: precipitation in inches;  
pressure: sea level pressure in millibars;  
visib: visibility in miles;  
time_hour: date and time combined.

The size of this dataset is `r nrow(early_january_weather)` rows and `r ncol(early_january_weather)` columns;  
and the mean temperature is `r mean(early_january_weather$temp)` degrees in Fahrenheit.




